### 2016-03-14 ch02-qlogms/excitation-design.tex
Add pole information initial model BK1613

\section{Measurements} 
\label{sec:excitation:measurement}
  \subsection{Setup}
    \label{sec:excitation:measurement:setup}
    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.

    The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
    According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
    A first guess to realize such a filter is a sixth-order Chebyshev band-pass filter of Type I~\citep{Zverev1967} for which the poles have a damping that is larger than $0.09$.
    %TODO: datasheet FRF?, pzmap with \damping shown, evt. tabel: per pool-paar: \wn ifv \wc, \damping
    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis}~\citep{FDIDENT}.
    The initial estimate was a sixth-order band-pass type I Chebyshev filter~\citep{Zverev1967} that conformed to the information given in the datasheet~\citep{datasheet_bk1613} to aid convergence to a good optimum.

>>>>

\section{Measurements} 
\label{sec:excitation:measurement}
  \subsection{Setup}
    \label{sec:excitation:measurement:setup}
    To show that this methodology also works for more complicated systems, we measured the frequency response functions of a \bruelkjaer{} Type 1613 Octave Filter Set using a National Instruments Elvis~II board driven by \labview.

    The \BK~1613 contains a set of eleven analog passive band-pass filters with center frequencies $\fc$ that are logarithmically distributed between $31.5\unit{Hz}$ and $31.5\unit{kHz}$ inclusive.
    According to its manual~\citep{datasheet_bk1613}, a $0.5\unit{dB}$ ripple with three resonances is present in the pass-band and the $3\unit{dB}$ break frequencies are located at $\frac{\fc}{\sqrt{2}}$ and $\fc \sqrt{2}$.
    This leads to a transfer function

    This leads to a sixth-order Chebyshev band-pass filter of Type~I~\citep{Zverev1967} given in the transfer function
    \begin{equation}
       G_{\mathrm{init}}(s) \approx 
      \frac{0.15922 s_{\mathrm{n}}^3 }{ s_{\mathrm{n}}^6 + 0.759 s_{\mathrm{n}}^5 + 3.564 s_{\mathrm{n}}^4 + 1.678 s_{\mathrm{n}}^3 + 3.564 s_{\mathrm{n}}^2 + 0.759 s_{\mathrm{n}} + 1}
      \label{eq:excitation:bk1613:tf-init}
     \end{equation}
     where $s_{\mathrm{n}} \isdef s \wc^{-1}$ and $\wc=2\pi \fc$ is the center frequency of the respective filter.
     It can be seen from \tabref{tbl:excitation:bk1613:poles} that each pole has $\damping \geq 0.09$.
    Since the different pole pairs that constitute such a filter have a different damping, this is an ideally suited system to evaluate the proposed method.
    The `shape' of the transfer function of the different filters is nominally identical, which allows for an easy visual comparison between the model uncertainty of the different filters.

    \begin{table}[b]
      \centering
      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter with center frequency $\wc$.}
      \label{tbl:excitation:bk1613:poles}
      \begin{tabular}{crr}
        \toprule
        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} \\
        \midrule
        $-(0.067 \pm 0.733j)\wc$ & $0.091$ & $0.736\wc$ \\ 
        $-(0.190 \pm 0.982j)\wc$ & $0.190$ & $\wc$ \\ 
        $-(0.123 \pm 1.350j)\wc$ & $0.091$ & $1.36\wc$ \\ 
        \bottomrule
      \end{tabular}
    \end{table}

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis}~\citep{FDIDENT}.
    To aid convergence to a good optimum, the initial estimate was a sixth-order band-pass type I Chebyshev filter given in \eqref{eq:excitation:bk1613:tf-init}.
